---
title: "Hilgard et al 2019"
author: Lincoln J Colling
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: FALSE
    citation_package: biblatex
documentclass: "article"
biblio-style: "apa"
classoption: ["a4paper","12pt"]
bibliography: ['references.bib','hilgard.bib']

header-includes:
  - \usepackage{pdflscape}
  - \usepackage{makecell}
  - \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
xfun::pkg_attach2("tidyverse",
"knitr",
"kableExtra",
"rmarkdown",
"bookdown",
"bib2df")

remotes::install_github("ljcolling/ODPHelper", upgrade = 'never')
options(kableExtra.latex.load_packages = TRUE)
hilgard <- readRDS("../made/hilgard.Rdata")
hilgard_download <- readRDS("../made/hilgard_download_info.Rdata")
readr::write_lines(unlist(hilgard$session_info$citations), path = "hilgard.bib")
library(ODPHelper)
as_tibble <- as_data_frame
keys = keys_from_session(hilgard$session_info$citations)
keys <- keys[!(keys %in% "R-ODPHelper")]
```

\newpage

# Introduction

This documents contains the reanalysis of the following paper:

Hilgard, J., Engelhardt, C. R., Rouder, J. N., Segert, I. L., & Bartholow, B. D. (2019). Null Effects of Game Violence, Game Difficulty, and 2D:4D Digit Ratio on Aggressive Behavior. *Psychological Science, 30*(4), 606–616.

@Hilgard provided analysis code along with their data. Therefore, to reproduce their results we simply tried to re-run their analysis code. The provided code was not able to successfully run on a recent install of **R** (version 4.0.0) with the most recent versions of Tidyverse. This failure was at least partly a result of breaking changes to the **dplyr** package. @Hilgard also provided a session information output with the **R** version and the package versions they used. However, it turned out that re-creating their exact enviroment was not trivial. Therefore, we instead decided to employ `r hilgard$session_info$sessionInfo$R.version$version.string` with all packages installed from a timestamped version of MRAN (date: `r str_remove(hilgard$session_info$cran,"https://mran.microsoft.com/snapshot/")`).

The analysis code is available at [https://github.com/ljcolling/odp-hilgard](https://github.com/ljcolling/odp-hilgard). This document is automatically built. To manually build this document, clone the git repository and run `make all`.

## Data download

A total of `r length(hilgard_download$files)` files was downloaded from [`r hilgard_download$files`](`r hilgard_download$files`). The downloaded files the MD5 hashes are shown in Table \@ref(tab:hilgardtable1).

```{r hilgardtable1, echo=FALSE}
tibble::tibble(`File name` = stringr::str_remove_all(names(hilgard_download$hashes),"./data/"), `MD5 Hash` = hilgard_download$hashes) %>%  knitr::kable(digits = 3, booktabs = T, caption = "Files downloaded for Hilgard et al. (2019)", escape = T, format = "latex") %>%
  kableExtra::kable_styling(latex_options = "scale_down") 
```

# Building files

We were able to successfully built all the requires results files. The list of files we attempted to build and whether they were successfully built is shown in Table \@ref(tab:hilgardtable2).

```{r hilgardtable2, echo=FALSE}
hilgard$built_files %>% magrittr::set_colnames(c("Filename","Successfully built")) %>%  knitr::kable(digits = 3, booktabs = T, caption = "Files downloaded for Hilgard et al. (2019)", escape = T, format = "latex", linesep="") %>%
  kableExtra::kable_styling(latex_options = "scale_down") 
```


# `R` information {-}

We performed our analysis on `r hilgard$session_info$sessionInfo$R.version$version.string` with all packages installed from a timestamped version of MRAN (date: `r str_remove(hilgard$session_info$cran,"https://mran.microsoft.com/snapshot/")`). The following R packages were used: `r paste0(map_chr(keys, function(x) glue::glue("@{x}")), collapse = ", ")`.


# References {-}
